Autocorrelation in Sparse Distributed Memory

### 2019-07-17 paperIEEE.tex
footnotes
Papaer
wtf

\section{Neurons as pointers}

@@

\section{Read operation}

In his work, Kanerva proposed and analyzed a read algorithm called here Kanerva's read. His read takes all activated hard locations counters and sum them. The resulting bitstring has bit $1$ where the result is positive, bit $0$ where the result is negative, and a random bit where the result is zero. In a word, each bit is chosen according to all written bitstrings in all hard locations, being equal to the bit more appeared. Table \ref{tab:kanerva-read} shows an example of Kanerva's read result bitstring.

@@

Our conclusion is that this work is of special relevance as it brings about some \emph{systemwide properties} that models need to take into account.  The first decision choice involved in building a system with SDM regards the size of $n$, the number of dimensions of the memory.  Here, complementing the work of XXXXXXXX, we show that as $n$ grows, autocorrelation tends to $0$.  But recall that as $n$ grows, the size of the critical distance also tends to $0$.  It is therefore crucial to select a value for $n$ in which the model will retain its convergence properties, with the understanding of the possible effects brought about by autocorrelation.   Systemwide properties such as these affect the entire behavior of the model and, as such, should always be taken into account by theoreticians and modelers alike.

@@

\begin{IEEEbiography}[
  {
  \includegraphics[width=1in,height=1.25in,clip]{./Chapters/Linhares.jpg}
  }
  ]
{Alexandre Linhares} received the Ph.D. degree from the National Institute of Space Research, 2001. He is an Associate Professor at the Center of Behavioral Research, EBAPE / Getulio Vargas Foundation.  He has published ~30 papers in journals such as \emph{Artificial Intelligence, Applied Intelligence, Biological Cybernetics, Cognitive Science, Cognitive Systems Research, Computers & Operations Research, IEEE Transactions on Evolutionary Computation, Information Sciences, Frontiers in Human Neuroscience,} among others.
\end{IEEEbiography}

>>>>

\subsection{Neurons as pointers}

@@

\subsection{Read operation}

In his work, Kanerva proposed and analyzed a read algorithm called here Kanerva's read. His read takes all activated hard locations counters and sum them. The resulting bitstring has bit $1$ where the result is positive, bit $0$ where the result is negative, and a random bit where the result is zero. In a word, each bit is chosen according to all written bitstrings in all hard locations, being equal to the bit more appeared.

@@

Our conclusion is that this work is of special relevance as it brings about some \emph{systemwide properties} that models need to take into account.  The first decision choice involved in building a system with SDM regards the size of $n$, the number of dimensions of the memory.  Here, complementing the work of XXXXXXXX\footnote{check this}, we show that as $n$ grows, autocorrelation tends to $0$.  But recall that as $n$ grows, the size of the critical distance also tends to $0$.  It is therefore crucial to select a value for $n$ in which the model will retain its convergence properties, with the understanding of the possible effects brought about by autocorrelation.   Systemwide properties such as these affect the entire behavior of the model and, as such, should always be taken into account by theoreticians and modelers alike.

@@

\begin{IEEEbiography}[
  {
  \includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{./Chapters/Linhares.jpg}
  }
  ]
{Alexandre Linhares} received the Ph.D. degree from the National Institute of Space Research, 2001. He is an Associate Professor at the Center of Behavioral Research, EBAPE / Getulio Vargas Foundation.  He has published ~30 papers in journals such as \emph{Artificial Intelligence, Applied Intelligence, Biological Cybernetics, Cognitive Science, Cognitive Systems Research, Computers & Operations Research, IEEE Transactions on Evolutionary Computation, Information Sciences, Frontiers in Human Neuroscience,} among others.
\end{IEEEbiography}
